%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage{pifont}
\input{glyphtounicode}

\newcommand{\githubstars}[1]{[{\faGithubSquare}\,\ding{72}\,\textbf{#1}]}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\linespread{1.1}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE \scshape SeongRae Noh} \\ \vspace{1pt}
    \small
    \href{mailto:rhosunr99@korea.ac.kr}{\underline{rhosunr99@korea.ac.kr}} $|$
    \href{https://seongraenoh.github.io/}{\underline{seongraenoh.github.io}} $|$
    \href{https://www.linkedin.com/in/seongrae-noh-220b462b7/}{\underline{linkedin.com/in/seongrae-noh}} $|$
    \href{https://github.com/SeongRaeNoh}{\underline{github.com/SeongRaeNoh}}
\end{center}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C++} \\
     \textbf{Frameworks \& Tools}{: PyTorch, HuggingFace, LangChain, OpenRouter, OpenCV, Git, WandB, Docker, UnrealEngine5} \\
     \textbf{Language}{: Korean (Native), English (Advanced), Japanese (Intermediate)}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Researcher}{Dec. 2021 -- Feb. 2024}
      {KyungHee University, IIIXR Lab (Advisor: Prof. HyeongYeop Kang)}{Yongin, South Korea}
      \resumeItemListStart
        \resumeItem{Developed an LLM-based multi-agent system in the VirtualHome environment for embodied task planning and interaction.}
        \resumeItem{Synthesized urban layouts using generative models and visualized them in Unreal Engine.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \item
      \textbf{(CVPR 2026) Edit-As-Act: Goal-Regressive Planning for Open-Vocabulary 3D Indoor Scene Editing} \\
      \small\textbf{SeongRae Noh}, SeungWon Seo, Gyeong-Moon Park, HyeongYeop Kang
      \resumeItemListStart
        \resumeItem{Improved instruction fidelity by 20\% and semantic consistency by 43.1\% over prior methods; introduced the E2A Benchmark.}
        \resumeItem{Reframed open-vocabulary 3D scene editing as goal-regressive world-state planning for verifiable and physically consistent edits.}
      \resumeItemListEnd
    \vspace{2pt}
    \item
      \textbf{(ICLR 2026) From Assumptions to Actions: Turning LLM Reasoning into Uncertainty-Aware Planning for Embodied Agents} \\
      \small SeungWon Seo*, SooBin Lim*, \textbf{SeongRae Noh*}, Haneul Kim, HyeongYeop Kang
      \resumeItemListStart
        \resumeItem{Reduced inter-agent communication by 71.1\% while improving task performance by 8.6\%.}
        \resumeItem{Proposed uncertainty-aware scenario tree planning to convert latent LLM assumptions into robust multi-agent decisions.}
      \resumeItemListEnd
    \vspace{2pt}
    \item
      \textbf{(AAAI 2025 Oral) REVECA: Adaptive Planning and Trajectory-Based Validation in Cooperative Language Agents Using Information Relevance and Relative Proximity} \\
      \small SeungWon Seo*, \textbf{SeongRae Noh*}, Junhyeok Lee, SooBin Lim, Won Hee Lee, HyeongYeop Kang
      \resumeItemListStart
        \resumeItem{Achieved 47\% performance improvement in noisy environments and increased user preference by 73\%.}
        \resumeItem{Enabled robust cooperation via relevance-filtered memory, proximity-aware planning, and trajectory-based validation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Development of a Multimodal Information-Driven Service Agent Framework} (LG Electronics)}{2025 -- 2026}
      \resumeItemListStart
        \resumeItem{Developed a multimodal HVAC service agent framework that integrates LLM reasoning with visual and structured data to support context-aware engineer assistance.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Understanding Multimodal PDF Documents Using LLMs} (LG Electronics)}{2025}
      \resumeItemListStart
        \resumeItem{Built an LVLM-based system for understanding multimodal HVAC PDF documents, enabling structured extraction and cross-modal reasoning over text, tables, and figures.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KyungHee University}{Yongin, South Korea}
      {Integrated MS-Ph.D. in Computer Science, IIIXR LAB (Advisor: Prof. HyeongYeop Kang)}{2024 -- Present}
    \resumeSubheading
      {KyungHee University}{Yongin, South Korea}
      {B.S. in Computer Science}{2020 -- 2024}
  \resumeSubHeadingListEnd


%-----------HONORS \& AWARDS-----------
\section{Honors \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{2025} -- AAAI Student Scholarship, AAAI \\
     \textbf{2024} -- Teaching Assistance Scholarship, Kyung Hee Univ. (Computer Graphics, Game Engine Basics) \\
     \textbf{2023} -- Pearl Abyss Fellowship (Project: Urban Building Block Generation) \\
     \textbf{2022} -- 2nd place on KHU Software Convergence Inter-Club Competition for COVID-19 Recovery Initiatives \\
     \textbf{2021} -- Pearl Abyss Fellowship (Project: Procedural Village Generation)
    }}
 \end{itemize}


%-----------ACADEMIC SERVICE-----------
\section{Academic Service}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Reviewer}{: ICML (2026), ACM MM (2025), Scientific Reports (2025)} \\
     \textbf{Student Volunteer}{: AAAI (2025)}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
